\chapter{Changelog}
\begin{chapquote}{Karl Lagerfeld}
``What I like about photographs is that they capture a moment that’s gone forever, impossible to reproduce.''
\end{chapquote}

This work is only a momentary snapshot in time and subject to change. Future revisions will be updated as errors are found and lab-gremmlins have been evicted. If an error is found in this work, the reader is encouraged to either send an email to \url{patrick.baus@physik.tu-darmstadt.de} or file a bug report over at Github. Do note, the author has mischievously hidden some errors and typos in this work for the observant reader to find. The latest version (and all others) can always be found by navigating to \url{https://github.com/PatrickBaus/phd_thesis} or using the QR code below.
\begin{center}
    \qrcode{https://github.com/PatrickBaus/phd_thesis}
\end{center}

\begin{center}
    \begin{minipage}{0.8\linewidth}
        \centering
        Current version: \versionNumber
    \end{minipage}%
\end{center}

\begin{center}
    \begin{xltabular}{0.95\textwidth}{ll>{\raggedright\arraybackslash}X}
        Version& Date& Comment\\
        \hline
        0.9.0 &2023-06-20 & Initial release submitted as the doctoral thesis.\\
        0.10.0 &2024-07-09 & Updated plot colours to match the Seaborn 0.9.0+ style.\\
        0.11.0 &2024-07-09 & Changed downsampling algorithm from decimation to LTTB. Affected files: dgDrive\_supply\_filter\_bode.pgf, dgTemp\_longterm.pgf, dgTemp\_testmass.pgf, output\_impedance\_libbrecht\_hall.pgf. Increased number of points in the leakage plots. Use $3-\sigma$ for the uncertainty of the temperature coefficient.\\
        0.12.0 &2024-07-09 & Regenerated all plots to unify their dimensions.\\
        0.13.0 &2024-07.09 & Fixed typos and other errors found so far.\\
        0.14.0 &2024-07-09 & Updated APQ-Latex design template to a version based on tuda-ci 3.38.\\
        0.15.0 &2024-07-11 & Changed the y-axis of the flicker noise amplitude plot to make it looker bigger. Decimate the noise psd plots to improve the uncertainty towards higher frequencies. Fixed LNA background noise data. There was an incorrect gain setting applied. Fixed dgDrive\_output\_impedance\_comparison plot, because the sense resistor was not subtracted from the plotted results. This affected all devices but the DgDrive.\\
        0.16.0 &2024-07-12 & Fixed simulated LNA noise floor. Fixed typos. Fixed the siunitx preamble for all plots.\\
        0.17.0 &2024-07-13 & Updated Numpy and AllanTools to 2.0.0 and 2024.6.\\
        0.18.0 &2024-07-14 & Fixed citations. Added Matplotlib and ReactiveX. Cleaned up URLs.\\
        0.19.0 &2024-07-15 & Reduced font size of the DVI connector labels.\\
        0.20.0 &2024-07-15 & Bump TeX Live to 2023.
    \end{xltabular}
\end{center}
